Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
add conclusions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@704 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  Here we added 4
new factors in comparison to the six factor experiment. The newly
added factors were \emph{weight}, \emph{nr. of doors},
\emph{nr. of seats} and \emph{fuel consumption}. We used the same
approach here as in the previous experiments to calculate the average
value for the new factors. The average values can be seen in the
planning matrix in appendix \ref{appB}. With 10 factors the amount of
runs were $2^10$. This results in 1024 number of runs which made the
planning matrix too big to show here.

@@

>>>>

\subsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  Here we added 4
new factors in comparison to the six factor experiment. The newly
added factors were \emph{weight}, \emph{nr. of doors},
\emph{nr. of seats} and \emph{fuel consumption}. We used the same
approach here as in the previous experiments to calculate the average
value for the new factors. The average values can be seen in the
planning matrix in appendix \ref{appB}. With 10 factors the amount of
runs were $2^{10}$. This results in 1024 number of runs which made the
planning matrix too big to show here.

@@

\section{Conclusions}

We recommend that both alternatives should be used together for
representing complex products. % TODO: Spiser ikke helt denne
Using only CO there should be done some alterations to reduce
bottleneck issues. We would not recommend using the data represented
by Renault today, because it is not robust enough and has a too long
response time for bigger operations.  It is also important that the
data representation is done properly to ensure readability for both
humans and machines.  Today, the Renault representation is neither
very understandable for machine nor for human. This is reflected in
the discussion about the application development.  The results from
the experiments done against the application shows that the current
representation is not feasible with today's performance standards and
user expectations. This is the area where most of the workload is on
the use of the ontologies.  This means that for a third party user VSO
in conjunction with COO are the best solution to work with product
models. However, this approach is limited to only represent data about
car models. It would also require some reasoning to be effective, but
with the technology and knowledge today that should not be a to
difficult issue. For other users wanting to represent constraints
between product models, CO can be a viable options if the proper
alterations is done. It can be very useful when working with several
data domains, but then the compatibility issue has to be solved.  One
solution could be to use the compatibility approach that COO
offers. This would result in adding several new triples in each
lexicon to avoid the configuration traversals.  It would also add the
need for reasoning to be effective, which is opposite of what Renault
proposed. If the compatibility issue is solved we believe the
performance can be feasible for almost every scenario. It will demand
more from the third party user, but can utilize more than just data
about car models. To make it even more effective, there should be done
several other alterations to both the representation and the ontology
as discussed in Section \ref{Alterations}.

Our recommendation is based on giving the user freedom to query the
data in several ways.  A future goal would be to do a more thorough
test of the ontologies for all possible scenarios, since the
versatility of the ontologies are huge. We believe that ultimately the
data from manufacturers and others can be profitable for several
online vendors and third party sites. Other manufactures of complex
product could profit from using semantic
technologies to represent their data.

Based on these investigations we conclude:
\begin{itemize}
 \item Both ontology approaches can be useful, but the generic needs several alterations to be more robust.
 \item The representation of the data is just as important as the ontology structure.
 \item Data should be as machine readable as possible, and properties denote more information, rather than classes if it is possible.
 \item To speed up the performance of the generic approach, the compatibility issue has to be resolved. One solution is to use the approach proposed in COO.
 \item Reasoning over the product models should be applied to increase efficiency and versatility.
\end{itemize}
